---
title: 'Problem Set #4'
author: "Hemanth Bharatha Chakravarthy"
date: "2/23/2019"
output: html_document
---

```{r setup, include=FALSE}
# Problem Set 4, Hemanth Bharatha Chakravarthy
# Because there are many plots here, the default option of 
# echo = FALSE is being set
knitr::opts_chunk$set(include = FALSE)
# Including the relevant libraries
library(tidyverse)
# I'm using default Tidyverse styles here
library(styler)
library(lintr)
library(ggplot2)
library(readr)
library(dplyr)
library(knitr)
# This package helps read our .csv file
library(readr)
library(janitor)
# These are a part of the visualization/stylistic choices for this project
library(ggridges)
library(viridis)
# Some useful computation is in lubridate
library(lubridate)
library(devtools)
library(gt)
# This project uses Harvard enrollment data obtained from the Registrar of the FAS
# The .xlsx file can be found on Canvas
# Loading the excel file skipping so that the titles of each column match those in the R df
# Cleaning names
polls <- read_csv("ps_4_elections-poll-nc09-3.csv", 
                  col_types = cols(
  .default = col_character(),
  turnout_scale = col_double(),
  turnout_score = col_double(),
  w_LV = col_double(),
  w_RV = col_double(),
  final_weight = col_double(),
  timestamp = col_datetime(format = "")
  )) %>% 
  clean_names()
# Note on style: I'm using traditional Tidyverse style and 
# This is auto-checked by `lintr::lint("test.R")````
```

# 1 Mad Libs

```{r mad_libs_q1}
# Checking to see if there are any nonsense values for response
# polls %>% 
#   group_by(response) %>% 
#   summarize()
# We know that all the values of response are fine based on the following being the result
# response
# <chr>
# 3				
# Dem				
# Rep				
# Und
dem_rep_count <- polls %>% 
  group_by(response) %>% 
  count() %>% 
  arrange()

gender_diff <- polls %>% 
  filter(gender != gender_combined) %>% 
  count()

race_white_diff <- polls %>% 
  filter(race_eth == "White", race_eth != file_race_black) %>% 
  count()

time_rep_dem_diff <- polls %>% 
  filter(response %in% c("Rep", "Dem")) %>% 
  arrange(timestamp) %>% 
  select(timestamp, response) 

time_diff <- time_rep_dem_diff[3,1] - time_rep_dem_diff[1,1] 
time_diff <- round(time_diff[1,1])
```
There were **`r dem_rep_count[2,2]`** respondents who supported the Democratic candidate.

There were **`r (dem_rep_count[3,2] - dem_rep_count[4,2])`**. more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (`gender` and `gender_combined`). There are **`r gender_diff[1,1]`** individuals for whom these variables have different values.

There are **`r race_white_diff[1,1]`** respondents listed as “White” under `race_eth` who are not listed as “White” under `file_race_black`.

The first `response` of Rep came **`r time_diff`** minutes (rounded to the nearest minute) before the first response of Dem.

# 2 Distribution of Votes Based on Race
```{r table_q1, include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
race <- polls %>% 
  select(race_eth, response, final_weight) %>% 
  filter(!is.na(response), 
        race_eth != "[DO NOT READ] Don't know/Refused",
        response %in% c("Dem", "Rep", "Und", "3")
        ) %>%  
  group_by(race_eth, response) %>% 
  summarize(total = sum(final_weight)) %>%
  spread(key = response, value = total) %>%
  # set NA as 0
  mutate_all(funs(replace(., is.na(.), 0))) %>% 
  ungroup() %>% 
  group_by(race_eth) %>% 
  mutate(y = Dem + Rep + Und + `3`) %>% 
  mutate(Dem = (Dem)/y,
         Rep = (Rep)/y,
         Und = (Und)/y) %>% 
  ungroup() %>% 
  select(race_eth, Dem, Rep, Und) %>% 
  slice(match(c("White", "Black", "Hispanic", "Asian", "Other"), race_eth))
  
# Table
race %>%
  gt(rowname_col = "race_eth") %>%
  tab_header(title = "Polling Results in North Carolina 9th Congressional District") %>%
  tab_source_note(
    source_note = "Data from GitHub User 'The Upshot'"
  ) %>% 
  cols_label(
    Dem = html("Democrat"),
    Rep = html("Republican"),
    Und = html("Undecided")
  ) %>%
  fmt_percent(
  columns = vars(Dem),
  decimals = 0) %>%
  fmt_percent(
  columns = vars(Rep),
  decimals = 0) %>%
  fmt_percent(
  columns = vars(Und),
  decimals = 0)
```
# 3 Education vs Turnout Weights 
```{r turnout_education_plot}

```


